---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geessbin

<!-- badges: start -->
<!-- badges: end -->

The geessbin function provides results of modified generalized estimating 
equations with bias-adjusted covariance estimators for longitudinal or clustered
data with binary outcomes.

## Installation

You can install the released version of geessbin from 
[CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("geessbin")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rtishii/geessbin")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(geessbin)
data(wheeze)

# analysis of PGEE method with Morel et al. covariance estimator
res <- geessbin(formula = Wheeze ~ City + Time, id = ID,
                repeated = Time, corstr = "ar1", data = wheeze,
                beta.method = "PGEE", SE.method = "MB")

# hypothesis tests for regression coefficients
summary(res)
```

