---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geessbin

<!-- badges: start -->
<!-- badges: end -->

The geessbin function analyzes small-sample clustered or longitudinal data using
modified generalized estimating equations (GEE) with bias-adjusted covariance
estimator. This function assumes binary outcome and uses the logit link
function. This function provides any combination of three GEE methods 
(conventional and two modified GEE methods) and 12 covariance estimators
(unadjusted and 11 bias-adjusted estimators).

## Installation

You can install the released version of geessbin from 
[CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("geessbin")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rtishii/geessbin")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(geessbin)
data(wheeze)

# analysis of PGEE method with Morel et al. covariance estimator
res <- geessbin(formula = Wheeze ~ City + factor(Age), data = wheeze, id = ID,
                corstr = "ar1", repeated = Age, beta.method = "PGEE",
                SE.method = "MB")

print(res)

# hypothesis tests for regression coefficients
summary(res)
```

